Titeln på avhandlingens språk

### 2023-04-09 body/part1/chapter1-introduction/background.tex
notes
cps

\subsection{\glsfmtlong{XR}}\label{background:xr}
\todo[inline]{Needs citations.}
\glsreset{XR}
\glsreset{AR}
\glsreset{VR}
\glsreset{MR}

@@

\subsubsection{\glsfmtlong{WCA}}\label{sec:background:wca}
\glsreset{WCA}

@@

% As with many other categories of \gls{AR} applications, the computational complexity of the processing of the real-time input data makes it unfeasible to do on wearable devices.
% This context-rich and latency-sensitive nature of \gls{WCA} inputs further makes this category of applications a prime candidate for offloading to the Edge.

\subsubsection{Emulation and simulation for \acs{XR}}
\todo[inline]{
    Section 1.1.2: This subsection is not very informative so far. Maybe first discuss extended reality, and then present a subsection on performance evaluation of systems, where simulation is a subsection, and experimentation is another subsection (and mathematical analysis is a third one). Focus on the usage of these concepts in the context of networked systems. Why do we need tools/approaches for performance evaluation, what are the advantages and disadvantages of different approaches, and also what is the historical context. You also need to have references. Finally, tables and figures are always welcome...
}

The terms \emph{emulation} and \emph{simulation} are often used interchangeably.
However, although both terms refer to methods of imitating and modeling systems, they are distinct in their goals, methods, and applications.

Emulation refers to the process of reproducing or mimicking the observed behavior of a system through another system, 
with the ultimate goal being the recreation of behavior that matches the original system as close as possible.
Emulations run in \emph{real time}, and can thus interact with real environments;
in turn, this means that emulations can be used to replace subcomponents of larger systems for research or benchmarking.
This method does not aim to model the original system, nor aim to understand its underlying behavior.

Simulation, on the other hand, is the process of modeling a system to study its behavior through the creation of a mathematical or logical model of the system.
The model can then be adjusted to simulate and better represent the original system in different scenarios and conditions.
Simulations run in entirely virtualized environments, and are not beholden to any real-time constraint.

Finally, these approaches differ as well in the level of accuracy each of them affords.
While simulation only attempts to approximate the behavior of the system in a given context, emulation aims to represent as close to a perfect copy of the observed behavior of the system.
The former is therefore employed when a general understanding of the system is sufficient, while the latter is used when precision is required.
However, thanks to its real time constraint and high degree of realism, emulation is typically more resource-intensive than simulation.
This means that emulation requires more processing power, memory, and storage space than simulation.

\subsection{\glsfmtlongpl{NCS}}\label{background:ncs}
\glsreset{NCS}

% \todo[inline]{
%     - Section 1.1.4: Goes again in the right direction, but details are missing/off. First of all, NCS is really a research direction, not necessarily a system type (every control system is more or less networked, but networking effects have not been always captured in the theoretical analysis/design of the controller). Second, maybe you stress more the working principle in terms workloads and requirements. In a sense, you can work out a pattern how you structure the discussion in Section 1.1.3, and reuse that pattern to a large extent in 1.1.4, that would be neat (both are closed-loop applications with a lot of similar, but also some different properties and requirements). 
% }

>>>>

\subsection{Performance evaluation of networked systems}
\todo[inline]{
    Too vague.
    Performance of networked systems.

    Look into book and use it as background.
    Something we can cite.
    2-3 pages.
}
\todo[inline]{
    Write.
}

\subsection{Closed-loop feedback systems enabled by Edge Computing}

\todo[inline]{
    Needs a better title.
    NCS and WCA?\@ Put everything under CPS?\@
    Closed-loop feedback systems.
}

\todo[inline]{
    Rework structure a bit.
}

\subsubsection{\glsfmtlong{XR}}\label{background:xr}
\todo[inline]{Needs citations.}
\glsreset{XR}
\glsreset{AR}
\glsreset{VR}
\glsreset{MR}

@@

\paragraph{\glsfmtlong{WCA}}\label{sec:background:wca}
\glsreset{WCA}

@@

\subsubsection{\glsfmtlong{CPS}}
\glsreset{CPS}

The term \gls{CPS} applies to a range of systems in which the computational world is tightly integrated with the physical world.
\glspl{CPS} are designed to monitor, control, and optimize physical processes.
By continuously monitoring and analyzing data from the physical components, \gls{CPS} can make decisions and take actions to optimize the system's performance.
For example, a \gls{CPS} controlling a building's heating, ventilation, and air conditioning system may adjust the temperature based on occupancy patterns, external weather conditions, and energy consumption goals.

\glspl{CPS} have acquired increasing importance in a wide range of industries due to their potential to enable greater efficiency, safety, and reliability in complex processes.
Examples of such applications of \glspl{CPS} include smart grids, \acs{ITS} and autonomous vehicles, and smart health monitoring.
A \emph{smart grid} is a \gls{CPS} that enables two-way communication between power generation, distribution, and consumption systems.
Smart grids can thus dynamically and in real-time adjust the distribution of power based on demand and supply conditions.
\glsreset{ITS} An \gls{ITS} is a system that integrates compute, monitoring, and communication in the context of a transportation system.
\glspl{ITS} enable real-time traffic monitoring and management, route optimization, and integration of autonomous vehicles.
These systems aim to optimize the management of transportation infrastructure and improve the safety, efficiency, and reliability of transportation systems.
Finally, \emph{smart health monitoring} is an application of \glspl{CPS} in which wearable devices equipped with sensors and communication capabilities collect real-time data on patients' vital signs, activity levels, and medication adherence.
This data can then be analyzed to provide alerts to healthcare providers, improve diagnoses, and facilitate early intervention.

Although these systems can enable greater efficiency, safety, and reliability in complex processes, the adoption of \glspl{CPS} faces several technical, social, and regulatory issues.
One of the key technical challenges relates to the reliability and safety of \glspl{CPS}.
As these systems tightly integrate physical and computational components, a failure in one component can have significant consequences.
As exemplified above, key use-cases for \glspl{CPS} include critical infrastructure such as power grids, transportation systems, and healthcare monitoring systems.
Any failure in these systems can have serious consequences for public safety and well-being.
Furthermore, \glspl{CPS} require strict security and confidentiality, given the sensitive data in these systems.
Developing CPS that are resilient to attacks and failures, as well as developing methods for testing and verifying their safety, is therefore a major research challenge.

\paragraph{\glsfmtlongpl{NCS}}\label{background:ncs}
\glsreset{NCS}

### 2023-04-09 body/part1/chapter2-relatedwork/key_contributions.tex
cps

\section{Scope \& overview of the included publications}

This dissertation presents a methodology for the study of feedback-loop \gls{CPS} systems deployed on Edge Computing and studies its potential applications and implications.
This methodology is based on the emulation of the desired application workload on top of the actual Edge infrastructure, including backend computing hardware and network technology used for client-server communication.
We do not in any way claim that this methodology is the best approach to studying these systems, but rather that it is a \emph{valid} approach able to produce accurate and representative results.

\input{tables/scope}

The scope of \gls{CPS} systems is vast and diverse, making it unfeasible to investigate all possible variations of these systems in this work. 
Instead, we opt to study a representative subset of future applications that could potentially leverage Edge Computing resources to provide innovative solutions: \gls{WCA} and \glspl{NCS}.
By considering these two application domains, we demonstrate the applicability of our methodology and showcase its efficacy.
\Cref{tab:scope} presents an overview of the scope of this dissertation, and in the following we will summarize the contributions and limitations of each included publication.

>>>>

\section{Overview of the included publications}

\todo[inline]{
    first main contribution: introduce the idea of emulating the physical part of a CPS when it comes to experimental evaluation running over an integrated communication and computation infrastructure.
    when we do that, we avoid many of the complications of experimental evaluation of these systems
    in combination with Ainur, is a very elegant proposition
    what is not currently captured precisely is that the approach is for the whole system (app + infra)
    Need to mention the emulation
    elegant and contemporary approach to efficient and repeatable evaluation of CPS

    second contribution:
    question of to which degree the emulation needs to capture certain details of the physical world?
    to which degree is emulation ``good enough''?
    for WCA specifically we propose a relatively detail of human user behavior based on empirical data
    evaluate to which extent the emulation is ``good enough'' by optimization of these systems

    Mention software, then we are on the safe.
}

### 2023-04-09 body/part1/chapter2-relatedwork/scope.tex
cps

>>>>

\todo[inline]{
    Emphasize that apps are standing for a new class of application class that the community is interested in developing.
    Why?
    Utility.
    Weave into intro and scope.

    Not just a random mashup.
    Relevance of the combination!

    Prime reason for experimental evaluation.
    Capture effects of compute, network, and design of the application.
    Hard to capture otherwise.

    Build argument in state of the art that there is no current satisfying way to address this.
    Potentially orders of magnitude off.

    In scope: interested in meaningful performance evaluation (i.e.\ capture all the complexity!) Make sure we note this.
    Show how apps and system are intimately related to each other and complex to evaluate.
    Where do complexities arise.
    Understanding system performance is key and complex.

    Scope: define the challenges.
}
